### 2022-04-25 draft.tex
Deploying to gh-pages from @ EcoComplex/TrophicResourcesEdaphic@63d956c9f58193bd17946d6bc33fbe5e1d6c4d68 🚀

Víctor Nicolás Velazco\textsuperscript{1,2}, Carlos Eduardo
Coviella\textsuperscript{1,2}, Liliana Beatriz
Falco\textsuperscript{1,2}, Leonardo Ariel Saravia\textsuperscript{3,4}
--- output: pdf\_document: latex\_engine: xelatex

documentclass: article geometry: - vmargin=1in - hmargin=1in
header-includes: -

\usepackage{pdflscape,booktabs}

\begin{itemize}
\item
  \newcommand{\blandscape}{\begin{landscape}}
\item
  \newcommand{\elandscape}{\end{landscape}}

  \begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
\end{itemize}

>>>>

Víctor Nicolás Velazco\textsuperscript{1,2}, Carlos Eduardo
Coviella\textsuperscript{1,2}, Liliana Beatriz
Falco\textsuperscript{1,2}, Leonardo Ariel Saravia\textsuperscript{3,4}
